Solar-Electric and Gas Powered, Long-Endurance UAV Sizing via Geometric Programming

### 2017-04-26 docs/paperin_review.tex
print to eps not pdf where possible

\begin{figure}[H]
 \begin{subfigmatrix}{2}% number of columns
     \subfigure[-30$^{\circ}$ latitude \label{f:windvsmonthS30}]{\includegraphics[natwidth=560,natheight=420]{windvsmonthS30.pdf}}
     \subfigure[+30$^{\circ}$ latitude \label{f:windvsmonthN30}]{\includegraphics[natwidth=560,natheight=420]{windvsmonthN30.pdf}}
 \end{subfigmatrix}
 \caption{\textbf{Winds peak at the winter solstice in Southern and Northern Hemispheres.\cite{wind}}}
 \label{f:windvsmonth}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=538,natheight=405]{altvswindhmin.pdf}
    \caption{\textbf{Aircraft must fly above $h_{\text{min}}$ to meet altitude requirement. Bands represent 80th, 90th and 95th percentiles.\cite{wind}}}
	\label{f:altvswindhmin}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=576,natheight=432]{latvswindN.pdf}
    \caption{\textbf{Wind speeds by latitude.  Bands represent 80th, 90th and 95th percentile winds.\cite{wind} }}
	\label{f:latvswind}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.8\textwidth,natwidth=480,natheight=200]{flowchart.pdf}
    \caption{\textbf{Process of constructing and solving a GP optimization problem. }}
	\label{f:flowchart}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.8\textwidth,natwidth=517,natheight=408]{simpleaircraft.pdf}
    \caption{\textbf{Blue and red are specific to the solar-electric and gas archictures respectively.  Black are shared characteristics.}}
	\label{f:simpleaircraft}
	\end{center}
\end{figure}

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.7\textwidth,natwidth=358,natheight=334]{wbreak.pdf}
   \caption{\textbf{Representative weight breakdown of both aircraft optimization models.}}
	\label{f:wbreak}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=536,natheight=405]{jho1polarfit1.pdf}
    \caption{\textbf{Posynomial fit (solid lines) to XFOIL data (circles).  (Log-space RMS error~=~0.00489.)}}
	\label{f:JH01polar}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.8\textwidth,natwidth=3242,natheight=1195]{capsparcross.pdf}
    \caption{\textbf{Cross sectional view of a cap spar.}}
	\label{f:capspar}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=528,natheight=405]{mtowvslat.pdf}
    \caption{\textbf{Gas archicture feasible for all latitudes. Next integer latitude for each solar-electric curve is infeasible.}}
    \label{f:latvsmtowtrade}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=527,natheight=405]{mtowvsendurance.pdf}
    \caption{\textbf{Endurance and size trade study for gas powered architecture.}}
	\label{f:mtowvsendurance}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=527,natheight=405]{battsolarcontour.pdf}
    \caption{\textbf{Contours of latitude. Reaching higher latitudes required better solar cells and batteries.}}
	\label{f:battsolarcontour}
	\end{center}
\end{figure}

@@

 \begin{figure}[H]
 \begin{subfigmatrix}{3}% number of columns
  \subfigure[35th Latitude, 80\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a80.pdf}}
  \subfigure[35th Latitude, 85\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a85.pdf}}
  \subfigure[35th Latitude, 90\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a90.pdf}}
  \subfigure[30th Latitude, 80\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a80.pdf}}
  \subfigure[30th Latitude, 85\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a85.pdf}}
  \subfigure[30th Latitude, 90\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a90.pdf}}
  \subfigure[25th Latitude, 80\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a80.pdf}}
  \subfigure[25th Latitude, 85\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a85.pdf}}
  \subfigure[25th Latitude, 90\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a90.pdf}}
 \end{subfigmatrix}
 \caption{\textbf{Maxtrix of minimum wing span solar-electric aircraft designs. Values of assumed constants are given throughout the text.}}
 \label{f:solarcontours}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=519,natheight=405]{windaltoper2.pdf}
 \caption{\textbf{Comparison of simplified and detailed structural models highlights trade between wing weight and air density.}}
 \label{f:altoper}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=555,natheight=415]{polarmission2.pdf}
    \caption{\textbf{Wind speed constraint moves lift to drag ratio off maximum $(C_L^{1.5}/C_D)$ point (plus signs). Solid lines are drag polars.}}
 \label{f:polarmission}
	\end{center}
\end{figure}

@@

    Using a trapezoidal integration of Equation~\eqref{e:solares}, the total available solar energy per unit area can be obtained for a given latitude and day of the year. Because only Equations~\eqref{e:solarreq}-\eqref{e:solarssolar} are GP compatible, the total solar energy per unit area per day, the length of the day and the length of the night are calculated from the latitude and the day of the year prior to an optimization solve.

@@

\begin{figure}[H]
 \begin{subfigmatrix}{2}% number of columns
     \subfigure[$C_L=0.0$\label{f:cpmin}]{\includegraphics[width=0.35\textwidth,natwidth=612,natheight=792]{cpmin.pdf}}
     \subfigure[$C_L=1.35$\label{f:cpmax}]{\includegraphics[width=0.35\textwidth,natwidth=612,natheight=792]{cpmax.pdf}}
 \end{subfigmatrix}
 \caption{\textbf{Pressure coefficient plots at the minimum and maximum expected $C_L$ at Reynolds number $Re=\num{3d5}$.}}
 \label{f:jhcps}
\end{figure}

>>>>

\begin{figure}[H]
 \begin{subfigmatrix}{2}% number of columns
     \subfigure[-30$^{\circ}$ latitude \label{f:windvsmonthS30}]{\includegraphics[natwidth=560,natheight=420]{windvsmonthS30.eps}}
     \subfigure[+30$^{\circ}$ latitude \label{f:windvsmonthN30}]{\includegraphics[natwidth=560,natheight=420]{windvsmonthN30.eps}}
 \end{subfigmatrix}
 \caption{\textbf{Winds peak at the winter solstice in Southern and Northern Hemispheres.\cite{wind}}}
 \label{f:windvsmonth}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=538,natheight=405]{altvswindhmin.eps}
    \caption{\textbf{Aircraft must fly above $h_{\text{min}}$ to meet altitude requirement. Bands represent 80th, 90th and 95th percentiles.\cite{wind}}}
	\label{f:altvswindhmin}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=576,natheight=432]{latvswindN.eps}
    \caption{\textbf{Wind speeds by latitude.  Bands represent 80th, 90th and 95th percentile winds.\cite{wind} }}
	\label{f:latvswind}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.8\textwidth,natwidth=568,natheight=154]{flowchart.eps}
    \caption{\textbf{Process of constructing and solving a GP optimization problem. }}
	\label{f:flowchart}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.9\textwidth,natwidth=447,natheight=265]{simpleaircraft.eps}
    \caption{\textbf{Blue and red are specific to the solar-electric and gas archictures respectively.  Black are shared characteristics.}}
	\label{f:simpleaircraft}
	\end{center}
\end{figure}

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.8\textwidth,natwidth=378,natheight=335]{wbreak.eps}
   \caption{\textbf{Representative weight breakdown of both aircraft optimization models.}}
	\label{f:wbreak}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=536,natheight=405]{jho1polarfit1.eps}
    \caption{\textbf{Posynomial fit (solid lines) to XFOIL data (circles).  (Log-space RMS error~=~0.00489.)}}
	\label{f:JH01polar}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.9\textwidth,natwidth=547,natheight=74]{capsparcross.eps}
    \caption{\textbf{Cross sectional view of a cap spar.}}
	\label{f:capspar}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=528,natheight=405]{mtowvslat.eps}
    \caption{\textbf{Gas archicture feasible for all latitudes. Next integer latitude for each solar-electric curve is infeasible.}}
    \label{f:latvsmtowtrade}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=527,natheight=405]{mtowvsendurance.eps}
    \caption{\textbf{Endurance and size trade study for gas powered architecture.}}
	\label{f:mtowvsendurance}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=527,natheight=405]{battsolarcontour.eps}
    \caption{\textbf{Contours of latitude. Reaching higher latitudes required better solar cells and batteries.}}
	\label{f:battsolarcontour}
	\end{center}
\end{figure}

@@

 \begin{figure}[H]
 \begin{subfigmatrix}{3}% number of columns
  \subfigure[35th Latitude, 80\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a80.eps}}
  \subfigure[35th Latitude, 85\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a85.eps}}
  \subfigure[35th Latitude, 90\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a90.eps}}
  \subfigure[30th Latitude, 80\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a80.eps}}
  \subfigure[30th Latitude, 85\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a85.eps}}
  \subfigure[30th Latitude, 90\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a90.eps}}
  \subfigure[25th Latitude, 80\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a80.eps}}
  \subfigure[25th Latitude, 85\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a85.eps}}
  \subfigure[25th Latitude, 90\% Wind Speed]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a90.eps}}
 \end{subfigmatrix}
 \caption{\textbf{Maxtrix of minimum wing span solar-electric aircraft designs. Values of assumed constants are given throughout the text.}}
 \label{f:solarcontours}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=519,natheight=405]{windaltoper2.eps}
 \caption{\textbf{Comparison of simplified and detailed structural models highlights trade between wing weight and air density.}}
 \label{f:altoper}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.6\textwidth,natwidth=555,natheight=415]{polarmission2.eps}
    \caption{\textbf{Wind speed constraint moves lift to drag ratio off maximum $(C_L^{1.5}/C_D)$ point (plus signs). Solid lines are drag polars.}}
 \label{f:polarmission}
	\end{center}
\end{figure}

@@

    Using a trapezoidal integration of Equation~\eqref{e:solares}, the total available solar energy per unit area can be obtained for a given latitude and day of the year. Because the equations in this appendix are not GP compatible, the total solar energy per unit area per day, the length of the day and the length of the night are calculated from the latitude and the day of the year prior to an optimization solve.

@@

\begin{figure}[H]
 \begin{subfigmatrix}{2}% number of columns
     \subfigure[$C_L=0.0$\label{f:cpmin}]{\includegraphics[width=0.45\textwidth,natwidth=792,natheight=612]{cpmin.eps}}
     \subfigure[$C_L=1.35$\label{f:cpmax}]{\includegraphics[width=0.45\textwidth,natwidth=792,natheight=612]{cpmax.eps}}
 \end{subfigmatrix}
 \caption{\textbf{Pressure coefficient plots at the minimum and maximum expected $C_L$ at Reynolds number $Re=\num{3d5}$.}}
 \label{f:jhcps}
\end{figure}
